---
title: "PA1_template"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Author: Sanjay Kumar
##Date: 03-Nov-2018
##1 Code for reading in the dataset and/or processing the data
```{r }
download.file("https://d396qusza40orc.cloudfront.net/repdata%2Fdata%2Factivity.zip",destfile="C:/Users/sanjayx/Desktop/coursera/activity.zip")
unzip("C:/Users/sanjayx/Desktop/coursera/activity.zip",exdir="C:/Users/sanjayx/Desktop/coursera/activity")
activity<-data.table::fread("C:/Users/sanjayx/Desktop/coursera/activity/activity.csv")
names(activity)
dim(activity)
#Remove null data
sum(is.na(activity))
sum(is.na(activity$date))
sum(is.na(activity$steps))
sum(is.na(activity$interval))
ok <- complete.cases(activity$date,activity$steps)
sum(!ok) 
activity1<-activity
activity <- activity[ok,]
#Validate null value
sum(is.na(activity))
```
##2 Histogram of the total number of steps taken each day
```{r, results='markup', warning=TRUE, message=TRUE}
library(lubridate)
dailysum <-aggregate(activity$steps,list(yday(as.POSIXlt(activity$date))), FUN=sum,na.rm=TRUE, na.action=NULL)
names(dailysum)<-c("yearday","steps")
hist(dailysum$steps,col="blue",main="Histogram for Daily Steps",xlab="Steps")
```
##3 Mean and median number of steps taken each day
```{r, results='markup', warning=TRUE, message=TRUE}
dailymean <-aggregate(activity$steps,list(yday(as.POSIXlt(activity$date))), FUN=mean,na.rm=TRUE, na.action=NULL)

dailymedian <-aggregate(activity$steps,list(yday(as.POSIXlt(activity$date))), FUN=median,na.rm=TRUE,na.action=NULL)
```
##4 Time series plot of the average number of steps taken
```{r}

plot.ts(dailymean$x,type="l",xlab="day",ylab="steps",main="Avergae no of steps taken",col="red")
```

##5 The 5-minute interval that, on average, contains the maximum number of steps
```{r}
maxstep<-max(activity$steps,na.rm=TRUE)

subset(activity,steps==maxstep)
```

##6 Code to describe and show a strategy for imputing missing data
```{r}
sum(is.na(activity1))
sum(is.na(activity1$date))
sum(is.na(activity1$steps))
sum(is.na(activity1$interval))
#install.packages("imputeTS")
library(imputeTS)
x<-na.mean(activity1)

dailysum <-aggregate(x$steps,list(yday(as.POSIXlt(x$date))), FUN=sum,na.rm=TRUE, na.action=NULL)

dailymean <-aggregate(x$steps,list(yday(as.POSIXlt(x$date))), FUN=mean,na.rm=TRUE, na.action=NULL)

dailymedian <-aggregate(x$steps,list(yday(as.POSIXlt(x$date))), FUN=median,na.rm=TRUE,na.action=NULL)
```
##7 Histogram of the total  steps taken each day after missing values are imputed
```{r}
hist(dailysum$x,col="blue",main="Histogram for Daily Steps after impute",xlab="Steps")
```
##8 Panel plot comparing the average number of steps taken per 5-minute interval across ## weekdays and weekends
```{r, results='markup', warning=TRUE, message=TRUE}
wdactivity<-subset(x,wday(x$date)<=5)
wendactivity<-subset(x,wday(x$date)>5)


weekdays <- c("Monday", "Tuesday", "Wednesday", "Thursday",  "Friday")
x$weekdays = as.factor(ifelse(is.element(weekdays(as.Date(x$date)),weekdays), 1, 0))

steps_i <- aggregate(steps ~ interval + weekdays, x, mean)

library(lattice)
xyplot(steps_i$steps~steps_i$interval|steps_i$weekdays,steps_i,xlab="Interval",ylab="steps",main="Steps(5min)",type="l")
```
`````
